Sequence Labeling for Gait Analysis using LSTM

### 2015-05-09 paper/paper.tex
Minor fixes

We took an iterative approach to build our neural network. Initially we implemented a low-complexity LSTM network, evaluated its performance by cross-validation, then attempted to improve its performance and robustness by adding additional components one at a time while evaluating performance.

@@

It is worth noticing that our implementation can do event detection in real time, both in the sense that it is computationally tractable and that our prediction is causal, relying only in past marker data. This makes our method unique, as we couldn't find anything on the literature that offered similar guarantees. Overall, the results we obtained are satisfying and we expect to polish them a little further before submitting them for publication in a gait research journal.

>>>>

We took an iterative approach to build our neural network. Initially we implemented a low-complexity LSTM network, evaluated its performance by cross-validation, then attempted to improve its performance and robustness by adding further components one at a time while evaluating performance.

@@

It is worth noticing that our implementation can do event detection in real time, both in the sense that it is computationally tractable and that our prediction is causal, relying only in past marker data. This makes our method unique, as we couldn't find anything in the literature that offered similar guarantees. Overall, the results we obtained are satisfying and we expect to polish them a little further before submitting them for publication in a gait research journal.
